Information within words in English, French and German speech

### 2019-07-01 surprisal/phoneme_writeup.Rmd
combined phoneme data and counts

```{r read-data}
all_data <- read_feather(here("Data/all_phonemes.feather"))
all_counts <- read_feather(here("Data/all_counts.feather"))
```

@@

```{r plot-helper}
plot_curves <- function(select_language = "English", select_rep = "letter", 
                        select_gram = "Unigram") {
  all_data %>%
    filter(language == select_language, rep == select_rep,
           gram == select_gram) %>%
    filter(word_length %in% 2:6) %>%
    ggplot(aes(x = order, y = mean_s)) +
    facet_grid(. ~ word_length, 
               labeller = as_labeller(function(x) paste0("Length ", x, " \n n = ", 
                                                         all_counts %>% 
                                                           filter(language == select_language,
                                                                  rep == select_rep, 
                                                                  length == x) %>%
                                                           pull(length)))) +
    geom_point() +
    geom_line() +
    xlab(paste0(str_to_sentence(select_rep), " Position")) +
    ylab("Average information") + 
    ggtitle(paste0("Information in ", select_language, " ", 
                   select_rep, "s by ",select_rep, " position - ", select_gram))
}
```

>>>>

```{r read-data}
all_data <- read_feather(here("Data/all_phonemes.feather"))
```

@@

```{r plot-helper}
plot_curves <- function(select_language = "English", select_rep = "letter", 
                        select_gram = "Unigram") {
  all_data %>%
    filter(language == select_language, rep == select_rep,
           gram == select_gram) %>%
    filter(word_length %in% 2:6) %>%
    ggplot(aes(x = order, y = mean_s)) +
    facet_grid(. ~ word_length, 
               labeller = as_labeller(function(x) paste0("Length ", x, " \n n = ", 
                                                         all_data %>% 
                                                           filter(language == select_language,
                                                                  rep == select_rep, 
                                                                  length == x) %>%
                                                           pull(length) %>%
                                                           unique()))) +
    geom_point() +
    geom_line() +
    xlab(paste0(str_to_sentence(select_rep), " Position")) +
    ylab("Average information") + 
    ggtitle(paste0("Information in ", select_language, " ", 
                   select_rep, "s by ",select_rep, " position - ", select_gram))
}
```
